---
title: Assignment_3
output: 
 pdf_document: default
 html_document: default
---

# Importing the Dataset
```{r}
data<-read.csv("universalBank.csv")
```

```{r}
summary(data)
```

```{r}
library(caret)
library(class)
library(dplyr)
library(ISLR)
library(psych)
library(FNN)
library(lattice)
```

#Removing ID and ZIP Code 
```{r}
data$ID <- NULL
data$ZIP.Code <- NULL
data$Education = as.factor(data$Education)
```

# creating a dummy dataset
```{r}
dummy_var <- as.data.frame(dummy.code(data$Education))
```

```{r}
names(dummy_var) <- c("Education_1", "Education_2","Education_3")
```

# Setting  education to NULL
```{r}
data$Education <- NULL
```

```{r}
data_2<- cbind(data, dummy_var)
```

# Dividing the dataset into train and test data
```{r}
set.seed(1)
train.index <- createDataPartition(data_2$Personal.Loan, p= 0.6 , list=FALSE)
valid.index <- setdiff(row.names(data_2), train.index)
train.dataset <- data_2[train.index,]
valid.dataset <- data_2[valid.index,]
```
# Generating the Test data
```{r}
data_customer<- data.frame(Age = 40,
                       Experience = 10,
                       Income = 84,
                       Family = 2,
                       CCAvg = 2,
                       Mortgage = 0,
                       Securities.Account = 0,
                       CD.Account = 0,
                       Online = 1,
                       CreditCard = 1,
                       Education_1 = 0, 
                       Education_2 = 1, 
                       Education_3 = 0)
                       
```


## Data normalisation
```{r}
train_norm <- train.dataset[,-7]
valid_norm <- valid.dataset[,-7]
data_norm <- data_customer

normalisation.values <- preProcess(train.dataset[, -7], method=c("center", "scale"))
train_norm <- predict(normalisation.values, train.dataset[, -7])
valid.normalisation.dataset <- predict(normalisation.values, valid.dataset[, -7])
data_norm <- predict(normalisation.values, data_norm)
```

```{r}
summary(train_norm)
```
# Performing Knn classification, using K=1
```{r}

knn_data <- class::knn(train = train_norm,test = data_norm,
                       cl = train.dataset$Personal.Loan, k = 1)

print(knn_data)
```


# Finding best K value
```{r}
k_value <- data.frame(k = seq(1, 10, 1), accuracy = rep(0, 10))
```


```{r}
for(i in 1:10) {
  knn_prediction <- class::knn(train = train_norm,
                         test = valid.normalisation.dataset,
                         cl = train.dataset$Personal.Loan, k = i)
  k_value[i, 2] <- confusionMatrix(knn_prediction,
                                       as.factor(valid.dataset$Personal.Loan))$overall[1]
}
which(k_value[,2] == max(k_value[,2]))
```


```{r}
k_value
```



##choosing k = 3
```{r}
knn_prediction <- class::knn(train = train_norm,
                       test = valid.normalisation.dataset,
                       cl = train.dataset$Personal.Loan, k = 3)

confusionMatrix(knn_prediction, as.factor(valid.dataset$Personal.Loan), positive = "1")
```

# Confusion matrix for the best k value =3

```{r}
newcustomer <- data.frame(Age = 40,
                            Experience = 10,
                            Income = 84,
                            Family = 2,
                            CCAvg = 2,
                            Mortgage = 0,
                            Securities.Account = 0,
                            CD.Account = 0,
                            Online = 1,
                            CreditCard = 1,
                            Education_1 = 0, 
                            Education_2 = 1, 
                            Education_3 = 0)

fitknn <-class::knn(train = train_norm,
                          test = newcustomer,
                          cl = train.dataset$Personal.Loan, k = 3)

fitknn
```
# Knn model tells that new customer will accept loan

```{r}
data<- read.csv("universalBank.csv")
```

# Loading packages

```{r}
library(ISLR)
library(psych)
library(caret)
library(FNN)
library(class)
library(dplyr)
library(lattice)

```

# Removing id and zipcode variables from the dataset

```{r}
data$ID <- NULL
data$ZIP.Code <- NULL
data$Education = as.factor(data$Education)

```

# Creating  dummy dataframe

```{r}
dummymod <- as.data.frame(dummy.code(data$Education))

```

##Renaming the data frame

```{r}
names(dummymod) <- c("Education_1", "Education_2","Education_3")

```

# Deleting education variable

```{r}
data$Education <- NULL 

```

##Main dataset

```{r}
data_2 <- cbind(data, dummymod)

```

#Partitioning  the dataset

```{r}
set.seed(1)
train.index <- createDataPartition(data_2$Personal.Loan, p= 0.5 , list=FALSE)
valid.index <- createDataPartition(data_2$Personal.Loan, p= 0.3 , list=FALSE)
test.index <- setdiff(row.names(data_2), union(train.index, valid.index))
                      
train.dataset <- data_2[train.index, ]
valid.dataset <- data_2[valid.index, ]
test.dataset <- data_2[test.index, ]

```

##Performing normalisation

```{r}
train_norm <- train.dataset[,-7]
valid.normalisation.dataset <- valid.dataset[,-7]
test.normalisation.dataset <- test.dataset[,-7]

normalisation.values <- preProcess(train.dataset[, -7], method=c("center", "scale"))
train_norm<- predict(normalisation.values, train.dataset[, -7])
valid.normalisation.dataset <- predict(normalisation.values, valid.dataset[, -7])
test.normalisation.dataset <- predict(normalisation.values, test.dataset[, -7])

```

## Performing Knn classification using K=3
```{r}
knn.test.pred <- class::knn(train = train_norm,
                       test = test.normalisation.dataset,
                       cl = train.dataset$Personal.Loan, k = 3)

knn.train.pred <- class::knn(train = train_norm,
                             test = train_norm,
                             cl = train.dataset$Personal.Loan, k = 3)

knn.valid.pred <- class::knn(train = train_norm,
                             test = valid.normalisation.dataset,
                             cl = train.dataset$Personal.Loan, k = 3)
```

##Confusion matrix for K=3

```{r}
confusionMatrix(knn.test.pred, as.factor(test.dataset$Personal.Loan), positive = "1")
confusionMatrix(knn.train.pred, as.factor(train.dataset$Personal.Loan), positive = "1")
confusionMatrix(knn.valid.pred, as.factor(valid.dataset$Personal.Loan), positive = "1")

```
